Thomas et al. 2025

### 2025-07-29 IndividualStudies/AT_2025.qmd
Removed text about how the AT_2025 data is a test page

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
# Read the data to a df

data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
:::::

## Data exploration

@@

## Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_download.csv dname="AT_ChemicalCommunications_2025">}}

>>>>

# Read the membrane data to a df
data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_membrane_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
::::: -->

### Data exploration

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 10))

### Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_membrane_download.csv dname="AT_ChemicalCommunications_2025">}}

:::{.callout-tip}

## Cytosolic Fraction

### Data visualization

```{r setup2, echo=FALSE, include=FALSE}

## intitialize libraries
library(here)
library(dplyr)
library(duckplyr)
library(ggplot2)
library(ggrepel)
library(emojifont)
library(dplyr)
library(tidyr)
library(docstring)
library(clusterProfiler)
library(org.Hs.eg.db)
library(enrichplot)
library(igraph)
library(ggtangle)
library(stringr)
library(crosstalk)
library(plotly)
library(grid)
library(readr)
library(rmarkdown)
library(gt)
library(DT)
library(heatmaply)
library(ggvenn)
library(scales)
library(htmltools)

# Read the membrane data to a df
data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_Cytosol_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

data |>
  arrange(hit_annotation) |>
  glimpse()

MAStandard(data)

:::
:::
<!-- 
### Gene Ontology Analysis

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
::::: -->

### Data exploration

@@

### Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_cytosol_download.csv dname="AT_ChemicalCommunications_2025">}}
